Data- and Ontology Paper: Quality Ontology for Parking Spots around Venues in Amsterdam

### 2016-04-21 milestone2/paper/paper.tex
More report

@@

\section{Section 3 - Related Work}
What other ontologies did you find that cover a similar domain. To what extent can they be reused. Have others (e.g. other students) developed similar datasets/ontologies that feed/meet your requirements, where do they fall short? Papers to look for are published at eg. ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.

>>>>

%TODO: is this novel? Website for accesible amsterdam does not have anything similar.

@@

New use cases explained in the introduction.

\section{Section 3 - Related Work}
\textit{What other ontologies did you find that cover a similar domain. To what extent can they be reused. Have others (e.g. other students) developed similar datasets/ontologies that feed/meet your requirements, where do they fall short? Papers to look for are published at eg. ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.}

 - Ontology for smart cities: \cite{komninos2015smart}
